Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa through development of a 3D spectral numerical coastal-flow model

### 2020-02-10 thesis_chapter_1.Rmd
minor corrections and housekeeping. reference list updated

---
title: Quantifying passive kelp rafting phenomena and connectivity of nearshore communities
  model
  around the coast of South Africa:Development of a 3D spectral numerical coastal-flow
author:
- RM Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  word_document:
    fig_caption: yes
    reference_docx: markdown/thesis_template.docx
    toc: yes
  html_document:
    df_print: paged
    theme: simplex
    toc: yes
  pdf_document:
    toc: yes
bibliography: references.bib
---

@@

## Buoyancy factors

>>>>

---
title: Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa through development of a 3D spectral numerical coastal-flow model
author:
- R Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  html_document:
    df_print: paged
    theme: simplex
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    fig_caption: yes
    reference_docx: markdown/thesis_template.docx
    toc: yes
bibliography: references.bib
---

@@
